BioTime

### 2021-03-11 data-raw/02_biotime_ids.Rmd
Resolve ID's appropriately

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
#load(here::here('data/BioTIME_grid_filtered.Rdata'))
bt_grid_col <- pins::pin_get("bt-grid-collate", board = "github_data")

@@

Add the unresolved ID to all the other ids and join with biotime data
```{r}
biotime_ids <- unres %>%
  left_join(biotime_ids) %>% #join ID's back with all the columns
  filter(acceptedNameUsageID %in% c(
    "ITIS:1026896", #accepted on the ITIS website
    "ITIS:172921",
    "ITIS:683209",
    "ITIS:527684",
    "ITIS:782604",
    "ITIS:159807"
  )) %>%
  bind_rows(biotime_ids %>% filter(!sort %in% unres$sort)) #join to resolved ID's, excluding the observations we resolved manually

@@

#save to cache
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
pins::pin(biotime_data, board = "github")
```

>>>>

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
bt_grid_col <- pins::pin_get("bt-grid-collate", board = "github")

@@

Add the unresolved ID to all the other ids and join with biotime data
```{r}
biotime_ids <- unres %>%
  left_join(biotime_ids) %>% #join ID's back with all the columns
  filter(acceptedNameUsageID %in% c(
    "ITIS:1026896", #accepted on the ITIS website 
    "ITIS:172921", 
    "ITIS:508923",
    "ITIS:527684", 
    "ITIS:782604", 
    "ITIS:159807", 
    "ITIS:28034"
  )) %>%
  bind_rows(biotime_ids %>% filter(!sort %in% unres$sort)) #join to resolved ID's, excluding the observations we resolved manually

@@

#save to cache
pins::pin(biotime_data, board = "github")
```
